%-------------------------
% CV (longer) in Latex
% Author: Kian Faizi
% Forked from: https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{soul}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kian Faizi} \\ \vspace{1pt}
    \small xxx-xxx-xxxx $|$ \href{mailto:kfaizi@ucsd.edu}{\ul{kfaizi@ucsd.edu}} $|$ 
    \href{https://www.kianfaizi.com/}{\ul{kianfaizi.com}} $|$
    \href{https://www.github.com/kfaizi/}{\ul{github.com/kfaizi}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{Aug. 2017 -- May 2021}
      {B.S. Molecular Biology, Minor in Mathematics (GPA: 3.76)}{La Jolla, CA}
      \resumeItemListStart
        \resumeItem{Selected coursework: Bioinformatics, Biophysics, Computational Linear Algebra, Gene Regulation, Genome Editing, Modeling, Statistics, Stochastic Processes}
      \resumeItemListEnd
    \resumeSubheading
      {International School of Kuala Lumpur}{Aug. 2013 -- May 2017}
      {I.B. Diploma, Earth Club President, Varsity Basketball Team Captain}{Kuala Lumpur, Malaysia}
  \resumeSubHeadingListEnd


%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lab Technician}{Nov. 2019 -- present}
      {Lab of Wolfgang Busch, Salk Institute for Biological Studies}{La Jolla, CA}
      \resumeItemListStart
        \resumeItem{Investigated cost-performance trade-offs in the \emph{Arabidopsis} root system using high-throughput phenotyping and graph-theoretic approaches}
        \resumeItem{Developed a Python GUI to segment time-series images of roots grown on agar plates; produced and analyzed approximately 1500 images}
        \resumeItem{Built a pipeline for co-expression network analysis of scRNA-seq data to identify root growth genes, in order to aid crop engineering efforts}
        \resumeItem{Measured ground-truth angles and radii from 3D point cloud data to aid development of phenotyping software}
      \resumeItemListEnd
    \resumeSubheading
      {Volunteer Research Assistant}{Nov. 2018 -- Nov. 2019}
      {Lab of Patrick Hsu, Salk Institute for Biological Studies}{La Jolla, CA}
      \resumeItemListStart
        \resumeItem{Created an automated pipeline to search over 20Tb of metagenome sequences for novel orthologs of Cas13d, an RNA-targeting CRISPR effector}
        \resumeItem{Assisted in conducting a pooled 150,000-guide CRISPR-Cas13d screen in K562s to study gRNA efficiency}
    \resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd



%-----------TEACHING EXPERIENCE-----------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Instructional Apprentice: Genetic Inquiry}{Aug. 2020 -- Dec. 2020}
      {Supervised by Dr. Stanley Lo, UCSD}{}
  \resumeSubHeadingListEnd

%----------PUBLICATIONS-------
\section{Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Curve skeleton extraction from 3D point clouds for high-throughput plant phenotyping.}}{}
          \resumeItemListStart
            \resumeItem{Illia Ziamtsov, \textbf{Kian Faizi}, and Saket Navlakha. \emph{In prep.}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Network design principles in the \emph{Arabidopsis} root system.}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Kian Faizi}, Matthieu Platre, Arjun Chandrasekhar, Saket Navlakha, and Wolfgang Busch. \emph{In prep.}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{A pooled CRISPR-Cas13d screen reveals guide RNA design principles.}}{}
          \resumeItemListStart
            \resumeItem{Silvana Konermann, \textbf{Kian Faizi}, Peter Lotfy, and Patrick Hsu. \emph{In prep.}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%----------POSTERS & PRESENTATIONS-------
\section{Posters and Presentations}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Co-expression analysis of single-cell RNA-seq data} $|$ \emph{Talk}}{Oct. 2020}
          \resumeItemListStart
            \resumeItem{Presented at the annual HDSI Research Conference}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Mining Genomes for RNA-Targeting CRISPR Effectors} $|$ \emph{Talk}}{Aug. 2019}
          \resumeItemListStart
            \resumeItem{Presented at the annual UCSD Summer Research Conference}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Metagenomic Discovery of Type VI-D CRISPR Effectors} $|$ \emph{Poster}}{June 2019}
          \resumeItemListStart
            \resumeItem{Presented at the annual UCSD Biology Student Research Showcase}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------HONORS AND AWARDS-----------
\section{Honors and Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Halicioglu Data Science Institute Scholarship} $|$ \emph{\$2,500 / UCSD}}{Dec. 2019}
          \resumeItemListStart
            \resumeItem{Project: \emph{Single-cell transcriptomics and web mining for rapid reverse genetics in plants}, proposed under Dr. Busch}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Eureka! Research Scholarship for Biological Sciences} $|$ \emph{\$5,000 / UCSD}}{June 2019}
          \resumeItemListStart
            \resumeItem{Project: \emph{Discovery and development of Type VI-D CRISPR effectors for transcriptome engineering applications}, proposed under Dr. Hsu}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Provost Honors} $|$ \emph{UCSD}}{quarterly}
       \resumeProjectHeading
          {\textbf{First Place Solo Performance} $|$ \emph{Sunway National Poetry Slam, Malaysia}}{Apr. 2016}
    \resumeSubHeadingListEnd

%-----------PROFESSIONAL ACTIVITIES-----------
\section{Professional Activities}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Member, Undergraduate Bioinformatics Club} $|$ \emph{UCSD}}{Nov. 2017 -- present}
      {}{}
      \resumeItemListStart
        \resumeItem{Collaborated with Illumina to develop digital resources for high school students interested in bioinformatics}
        \resumeItem{Helped organize the 2018 Faculty \& Industry Bioinformatics Symposium}
        \resumeItem{Volunteered in the club booth at SDSEF to educate the community about DNA sequencing technology}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Laboratory}{: Cell/tissue culture, molecular cloning, CRISPR screens, lentiviral transduction, optical microscopy} \\
     \textbf{Languages}{: Python, bash, JavaScript, HTML/CSS, R, Perl} \\
     \textbf{Organizational}{: Git, \LaTeX, conda, vim, Unix systems} \\
     \textbf{Libraries}{: BLAST+, pandas, NumPy, ScanPy, matplotlib, NetworkX} \\}}
 \end{itemize}


%-------------------------------------------
\end{document}